$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
generalize -> generalise

\begin{proof}[Proof (Sketch)]
  The proof is by induction on \textsc{Equals} $\eq{}$.
  Here we only consider the nontrivial base cases for $\constr{struct}$ and their symmetric variants.
  Full proof in \cite{Zalakain2020Agda}.
  We proceed by induction on \textsc{StructCong} $\eqeq$:
  \begin{itemize}
    \item
      Case $\constr{comp-assoc}$: trivial, as leftover typing is naturally associative.
    \item
      Case $\constr{comp-sym}$ for $\comp{P}{Q}$: we use framing (\autoref{thm:framing}) to shift the output context of $P$ to the one of $Q$; and the input context of $Q$ to the one of $P$.
    \item
      Case $\constr{comp-end}$: trivial, as the typing rule for $\PO$ has the same input and output contexts.
    \item
      Case $\constr{scope-end}$: we show that the usage annotation of the newly created channel must be $\lz$, making the proof trivial.
      In the opposite direction, we instantiate the newly created channel to a type $\unit$ and a usage annotation $\lz$..
    \item
      Case $\constr{scope-ext}$ for $\new \comp{P}{Q}$: we to show that $P$ preserves the usage annotations of the unused variable (\autoref{lm:types-unused}) and then use strengthening (\autoref{thm:strengthening}).
      In the reverse direction, we use weakening (\autoref{thm:weakening}) on $P$ and show that lowering and then lifting $P$ results in $P$ (\autoref{lm:lower-lift}).
    \item
      Case $\constr{scope-comm}$:
      we use swapping (\autoref{thm:swapping}), and for the reverse direction swapping and \autoref{lm:swap-swap} to show that swapping two elements in $P$ twice leaves $P$ unchanged. \qedhere
  \end{itemize}
\end{proof}
\subsection{Substitution}
\label{substitution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{generaliz* to generalis* everywhere}
\autoref{thm:subst-generalization} proves a generalized version of substitution, where the substitution $\subst{P}{j}{i}$ is on any variable $i$.
\autoref{thm:substitution} instantiates the generalized version to the concrete case where $i$ is $\constr{0}$, as required by subject reduction.
\todo{explain what i is 0 mean}

>>>>

\begin{proof}[Proof (Sketch)]
  The proof is by induction on \textsc{Equals} $\eq{}$.
  Here we only consider the nontrivial base cases for $\constr{struct}$ and their symmetric variants.
  Full proof in \cite{Zalakain2020Agda}.
  We proceed by induction on \textsc{StructCong} $\eqeq$:
  \begin{itemize}
    \item
      Case $\constr{comp-assoc}$: trivial, as leftover typing is naturally associative.
    \item
      Case $\constr{comp-sym}$ for $\comp{P}{Q}$: we use framing (\autoref{thm:framing}) to shift the output context of $P$ to the one of $Q$; and the input context of $Q$ to the one of $P$.
    \item
      Case $\constr{comp-end}$: trivial, as the typing rule for $\PO$ has the same input and output contexts.
    \item
      Case $\constr{scope-end}$: we show that the usage annotation of the newly created channel must be $\lz$, making the proof trivial.
      In the opposite direction, we instantiate the newly created channel to a type $\unit$ and a usage annotation $\lz$..
    \item
      Case $\constr{scope-ext}$ for $\new \comp{P}{Q}$: we to show that $P$ preserves the usage annotations of the unused variable (\autoref{lm:types-unused}) and then use strengthening (\autoref{thm:strengthening}).
      In the reverse direction, we use weakening (\autoref{thm:weakening}) on $P$ and show that lowering and then lifting $P$ results in $P$ (\autoref{lm:lower-lift}).
    \item
      Case $\constr{scope-comm}$:
      we use swapping (\autoref{thm:swapping}), and for the reverse direction swapping and \autoref{lm:swap-swap} to show that swapping two elements in $P$ twice leaves $P$ unchanged. \qedhere
  \end{itemize}
\end{proof}
\subsection{Substitution}
\label{substitution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\autoref{thm:subst-generalization} proves a generalised version of substitution, where the substitution $\subst{P}{j}{i}$ is on any variable $i$.
\autoref{thm:substitution} instantiates the generalised version to the concrete case where $i$ is $\constr{0}$, as required by subject reduction.
\todo{explain what i is 0 mean}
